% XeLaTeX can use any Mac OS X font. See the setromanfont command below.
% Input to XeLaTeX is full Unicode, so Unicode characters can be typed directly into the source.

% The next lines tell TeXShop to typeset with xelatex, and to open and save the source with Unicode encoding.

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[14pt]{extreport}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{a4paper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{url}
\usepackage{amsmath}

% Will Robertson's fontspec.sty can be used to simplify font choices.
% To experiment, open /Applications/Font Book to examine the fonts provided on Mac OS X,
% and change "Hoefler Text" to any of these choices.
  
\usepackage{fontspec,xltxtra,xunicode}
\defaultfontfeatures{Mapping=tex-text}
%\setromanfont[Mapping=tex-text]{Hoefler Text}
%\setsansfont[Scale=MatchLowercase,Mapping=tex-text]{Gill Sans}
\setmonofont[Scale=MatchLowercase]{Andale Mono}

\title{\huge{Estimating Real World Use of Image Steganography}}
\author{Ritesh Kumar Sinha\\ 1006510\\MSc(IT) 2010-2011}
\date{}                                           % Activate to display a given date or no date

\begin{document}
\maketitle

% For many users, the previous commands will be enough.
% If you want to directly input Unicode, add an Input Menu or Keyboard to the menu bar 
% using the International Panel in System Preferences.
% Unicode must be typeset using a font containing the appropriate characters.
% Remove the comment signs below for examples.

% \newfontfamily{\A}{Geeza Pro}
% \newfontfamily{\H}[Scale=0.9]{Lucida Grande}
% \newfontfamily{\J}[Scale=0.85]{Osaka}

% Here are some multilingual Unicode fonts: this is Arabic text: {\A السلام عليكم}, this is Hebrew: {\H שלום}, 
% and here's some Japanese: {\J 今日は}.


\pagenumbering{roman}
\tableofcontents

\chapter*{Acknowledgements}
I would like to thank my supervisor Dr. Timothy Storer for his endless patience, advice and assistance. 
\begin{abstract}
Steganography is the art and science  of hiding information in plain sight. This is accomplished by using an innocuous ``cover'' medium in which the data to be hidden is embedded using an algorithm known to the parties trying to communicate. The embedding algorithm is carefully chosen in such a way that it produces no noticeable changes in the cover medium. As an additional safeguard, the information to be transmitted may also be encrypted using a separate algorithm before it is embedded into to the cover medium to make detection even more difficult. \\
Digital image steganography provides a means of communication between parties wishing to share secrets in an environment where the use of other covert channels may arouse suspicion. A digital image file provides a suitable cover medium for embedding data as subtle changes in the file structure produce no visually identifiable changes in the image. All popular image formats (\emph{e.g.} JPEG, BMP, PNG, GIF) can be utilised as carriers for steganography. Freely available steganographic tools exploit properties unique to the particular image format while embedding data. This is done to minimise the possibility  of detection by visual inspection of the image.
\\ The detection of image steganography by visual inspection alone is difficult and impossible in non trivial cases, it is still possible to \emph{prove} that an image contains steganographic content with reasonable accuracy. Detection can be carried out by either testing the image for tell tale ``signatures'' of popular steganographic algorithms or by statistical analysis.  This project describes the design and implementation of an experimental system that
attempts to identify images that contain steganographic content from a random selection of JPEG images obtained from free classified advertisements. 
%\nocite{*} 
\end{abstract}
\pagenumbering{arabic}
\include{intro}
\include{survey}
%\include{dev}
%\include{eval}
%\include{conclusion}
\bibliographystyle{plain}
\bibliography{thesis}
\end{document}


